Exploration of clustering results for `r params$sample_id`

### 2024-08-14 analyses/cell-type-wilms-tumor-06/notebook-template/01-clustering.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook-template/01-clustering.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

```{r load}
filelist <- list.files(data_dir, full.names = TRUE)

# select the 40 Wilms tumor single nucleus folders only
filedir <- filelist[grepl(params$sample_id, filelist)]

file <- list.files(filedir)
file <- file[grepl("_processed.rds", file)]

# open the processed rds object
sce <- readRDS(paste0(filedir, "/", file))
```

@@

# Normalization
options(future.globals.maxSize= 8912896000000)
srat <- SCTransform(srat, verbose = F, conserve.memory = TRUE)

@@

Here, we open the table of marker genes marker-sets/CellType_metadata.csv. 
Note: we do not expect to have a clear and nice pattern of expression for all of the following markers in every tumor. 
This is just ti get a few idea.

>>>>

```{r load}
sample_dir <- file.path(data_dir, params$sample_id)
sample_files <- list.files(sample_dir)

file <- sample_files[grepl("_processed.rds", sample_files)]

# open the processed rds object
sce <- readRDS(file.path(sample_dir, file))
```

@@

# Normalization
srat <- SCTransform(srat, verbose = F, conserve.memory = TRUE)

@@

Here, we open the table of marker genes marker-sets/CellType_metadata.csv. 
Note: we do not expect to have a clear and nice pattern of expression for all of the following markers in every tumor. 
This is just to get a few ideas.
